Spontaneous Similarity Judgments of Musical Tones played with various Playing Techniques

### 2017-12-11 paper/lagrangeSpontaneousSimilarity2017.tex
starting with model

This model is chosen over more complex alternatives for the sake of simplicity. Deep convolutional networks could have been considered, but the learning stage inherent in this kind of methods did not seem relevant for this study. On contrary, the scattering transform can be conveniently parametrized to match the perceptual capabilities of the auditory system that do not change significantly among subjects. Also, more complex versions of the scattering like the joint time-frequency scattering and the spiral scattering are not considered in order to achieve a projection of reasonable dimensionality and for lack of evidence that those dimensions are useful to model the primary stage of the auditory system \cite{dau}.

>>>>

This model is chosen over more complex alternatives for the sake of simplicity. Deep convolutional networks could have been considered, but the learning stage inherent in this kind of methods did not seem relevant for this study. On contrary, the scattering transform can be conveniently parametrized to match the perceptual capabilities of the auditory system that do not change significantly among subjects. Also, more complex versions of the scattering like the joint time-frequency scattering \cite{waspaa} and the spiral scattering are not considered in order to achieve a projection of reasonable dimensionality and for lack of evidence that those dimensions are useful to model the primary stage of the auditory system \cite{dau}.
